### 2019-06-15 papers/journal/ex-vts.tex
First Update for revision

\subsection{Mammalian VTS}
\input{fig-mukund-vts}

The Figure~\ref{fig:mukund-vts} represent mammalian SNARE map
created by studying the wide array of literature.
% 
To construct the map, we have assumed that vesicles only contain a
single active v-SNARE, and we have attributed t-SNAREs and inactive
v-SNAREs that travel between compartments to one of the known vesicles
that go between the same source and target compartments.
%
In order to identify the active SNARE complex involved in any
particular vesicle fusion, we used two criteria.
%
The SNARE complex is formed \textit{in vivo}. In most papers, this is
determined by immunoprecipitation of the SNARE complex from the
relevant cell fraction.
%
Blocking SNARE complex formation (for example, using antibodies
against these SNAREs, or using cytosolic forms of these SNAREs) blocks
the specific transport step.
%
Note that these vesicles have been collected from multiple cell types, and
any given cell type is likely to contain only a subset of the vesicles in
the map.

@@

\input{fig-yeast-vts}

In Figure~\ref{fig:yeast-vts}, we present the yeast VTS.
%
We have borrowed the VTS from~\cite{burri2004complete}.
%
It has been adapted from the paper by
separating the v and the t SNAREs. 
%
It is clear that it is an incomplete description of the VTS.
%
For example, the inactive molecules were not reported in the reference.
%
We are currently searching for more literature that can help us complete
all known information about the VTS.
%

>>>>

\subsection{Mammalian VTS}
\input{fig5}

The Fig.~\ref{fig:mukund-vts} represent mammalian SNARE map
created by studying the wide array of literature.
% 
To construct the map, we have assumed that vesicles only contain a
single active v-SNARE, and we have attributed t-SNAREs and inactive
v-SNAREs that travel between compartments to one of the known vesicles
that go between the same source and target compartments.
%
In order to identify the active SNARE complex involved in any
particular vesicle fusion, we used two criteria.
%
The SNARE complex is formed \textit{in vivo}. In most papers, this is
determined by immunoprecipitation of the SNARE complex from the
relevant cell fraction.
%
Blocking SNARE complex formation (for example, using antibodies
against these SNAREs, or using cytosolic forms of these SNAREs) blocks
the specific transport step.
%
Note that these vesicles have been collected from multiple cell types, and
any given cell type is likely to contain only a subset of the vesicles in
the map.

@@

\input{fig6}

In Fig.~\ref{fig:yeast-vts}, we present the yeast VTS.
%
We have borrowed the VTS from~\cite{burri2004complete}.
%
It has been adapted from the paper by
separating the v and the t SNAREs. 
%
It is clear that it is an incomplete description of the VTS.
%
For example, the inactive molecules were not reported in the reference.
%
We are currently searching for more literature that can help us complete
all known information about the VTS.
%

### 2019-06-15 papers/journal/experiments.tex
Minor fix of ref
First Update for revision

%\externaldocument{sat-table}
%We have developed four different tools (\sattool, \smttool, \qbftool, \ourtool) for implementation of proposed encodings.
%
\noindent We have developed the {\vtstool} tool to conjecture the properties of the VTS (explained in Section 6). 
%
%
The {\vtstool} tool includes about 10,000 lines of code.
%
The tool is divided into three different blocks,
%
checking existential condition, checking the universal condition and performing synthesis on the incomplete VTS. 
%
The existential condition is subdivided into two subblocks, bounded model checking and constraint solving. 
%
We will refer to existential subblocks as {\sattool} and {\smttool}, universal block as {\qbftool} and synthesis block as {\ourtool}.
%

@@

%\textbf{{
\subsubsection{{\sattool} (Bounded model checker based tool)}
%}}
The $\fbmc$ encoding based on enumeration of paths (Section~\ref{enc:bmc}) for each variants of VTS is implemented in {\sattool}.
	%We have implemented the encodings for different variants of VTS (presented in section 6.2) using
The tool is based on CBMC, a successful bounded model checker, for C and C++ programs. 
%
%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
%
It verifies property for all the possible states, up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of the model is specified by the user and can be incrementally increased to the desired value.
%
%The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
%CBMC front end accepts

%We encode the problem using CBMC C-language front-end (CFE) interface with some special annotations called \textit{assumes} and \textit{assertions}.
%
%These annotations express constraints on the model and properties to be checked. 
%	
The vesicle transport network was modeled as a non-deterministic C-program manipulating an annotated graph. 
%
The special annotations \textit{assumes} and \textit{assertions} of CBMC's front end were used to express constraints on the model and properties to be checked. 
%
%The fusion rules and steady state properties were expressed as constraints using special annotations \textit{assumes}. 
%		
%The correspondence relationship between connectedness conditions and steady state were expressed as annotations \textit{assertions} to be checked. 
Using the tool's interface user can select the variation of the VTS, connectivity of the graph and other required parameters like an exploration depth.
%
The {\sattool} verifies the properties by first converting the constraints and properties into a Boolean formula and determine the satisfiability of the formula with the help of a SAT solver backend.
%
The satisfying model is translated into a human readable format and in case of a violation, the tool produces a readable counterexample.
%  following steps:
%	\begin{itemize}
%	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
%depth iff the Boolean formula is valid.
%	\item Check (using a SAT solver) validity of the verification condition. {\sattool} reports successful verification if the formula is found to be valid. If not, then {\sattool} produces a counterexample,
%an assignment to the variables of the model, that is a witness to the violation of the property.
%	\end{itemize}
For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat} and CryptoMiniSat~\cite{soos2016cryptominisat}.
% the winner of SAT 2015 Competition~\cite{balyo2016sat}.

@@

\subsubsection{{\ourtool} (QBF based synthesis tool)}
\input{synth-table}
The synthesis encodings (Section~\ref{enc:synth}) is implemented  in~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS using the {\qbftool} interface. 
%
The tool can synthesize the queries discussed earlier and also their combinations.
%The tool can not only synthesize the discussed queries, but also their combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
The tool returns a complete VTS with visual graph representation as an output to the user.

@@

\input{smt-table}

The minimal connectivity results for each variation of the existential condition are presented in Table~\ref{tab:smt-grph}.
%
The steady-state constraint requires that the structure of the graph is at least 2-connected. 
%
We found that 3-connectedness is the existential condition for the Boolean regulation model on vesicles, while 4-connectedness is the existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%
For all other constrained regulation models of VTS, the experimentation was unable to find any graphs representing the vesicle transport networks in the stable state.
%
This strongly suggests that no such graphs exist, as our graphs are of finite size, this does not amount to a  proof.

@@

%
The Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
%
For this comparison, we have fixed the total number of molecules minimum four times for each SNARE type of the node count. 
%
The maximum number of parallel edges is 2.
%
%For our analysis we relax the 3:1 requirement for the Q and R-SNARES and treat a Q-SNARE triple helix as a single complex as modelled in~\cite{shukla2017discovering}.
%
%The 
%
In the table M/O indicates the search results in out of memory, T/O indicates a time out and ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
%
As an example, the result of verifying the formula for variation C of 3-connected, 10 compartment graph took 1977.72 secs for a satisfying result.
%
In comparison, {\sattool} was unable to solve the instance and ran out of memory.
%
The recursive encoding also performed better for the cases where the instance was unsatisfiable (Variant A timing comparison).
%
Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the case of eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with the limits of our tools and found that {\smttool} was able to solve the constraints up to $18$ nodes.

\input{qbf-table}
%\textbf{Universal Condition:}

The Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
%
The result of the graph connectivity for each variation of the VTS is shown.  
%
For example, we found that the 3-connected graph satisfies the universal condition for the variation 2. 
%
Note that for this variation existential condition result was the 2-connected graph. 
%
For every other version, the results remained the same.
%
This implies that for every 3-connected graph there is a valid VTS that satisfies all the constraints of the system.
% 
For biological cells, this means that the whole space of 3-connected graphs is available for evolutionary exploration.
%
%The experimentations were done using two QBF solvers: \depqbf and \rarqbf.

%(there is a satisfying assignments to satisfy constraints of VTS) is valid VTS.   
%\textbf{Synthesis}:

We have applied~\ourtool~on seven partially defined VTSs.
%
The results are presented in Figure~\ref{tab:synth-graph} for both the solvers
\depqbf and \zthree.
%
To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
quantifier-free.
%
The first four and the sixth VTSs are synthetic but inspire from literature for
typical motifs in VTSs. 
%
The third VTS is a subgraph of the last VTS.
%
%
The fifth VTS is taken from~\cite{burri2004complete}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.  
%
The figure shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.

In the Figure~\ref{tab:synth-graph}, we report five synthesis queries.
%
The first one only adds new labeled edges to the graph.
%
We have ranked the all possible graph edits with the simple rank of
minimum updates.
% %
% Our tools were able to complete the graphs by adding five new edges
% and nine new molecules in 210s.
%
The second query adds new labels to the edge.
%
The third query synthesizes NNF Boolean functions only containing
$\land$ and $\lor$ gates for activity functions, while allowing
more edges to be added.
%
The result shows the basic template of 4 leaves and 3 gates.
%
To illustrate the versatility of our tool, the fourth query
synthesizes $3$-CNF functions (encoding not presented).
%
Finally, we report queries that allow both addition and deletion of edges and labels of node and labels.

>>>>

%We have developed four different tools (\sattool, \smttool, \qbftool, \ourtool) for implementation of proposed encodings.
%
\noindent We have developed the {\vtstool}\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}} tool to conjecture the properties of the VTS (Section~\ref{sec:encoding}). 
%
%
The {\vtstool} tool includes about 10,000 lines of code.
%
The tool is divided into three different blocks,
%
checking existential condition, checking the universal condition and performing synthesis on the incomplete VTS. 
%
The existential condition is subdivided into two subblocks, bounded model checking and constraint solving. 
%
We will refer to existential subblocks as {\sattool} and {\smttool}, universal block as {\qbftool} and synthesis block as {\ourtool}.
%

@@

%\textbf{{
\subsubsection{{\sattool} (BMC based tool)}
%}}
The $\fbmc$ encoding based on enumeration of paths (Section~\ref{enc:bmc}) for each variants of VTS is implemented in {\sattool}.
	%We have implemented the encodings for different variants of VTS (presented in section 6.2) using
The tool is based on CBMC, a successful bounded model checker, for C and C++ programs. 
%
%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
%
It verifies property for all the possible states, up to a certain ``depth”, a parametric limit on the size of the model.
%
The depth of the model is specified by the user and can be incrementally increased to the desired value.
%
%The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
%CBMC front end accepts

%We encode the problem using CBMC C-language front-end (CFE) interface with some special annotations called \textit{assumes} and \textit{assertions}.
%
%These annotations express constraints on the model and properties to be checked. 
%	
The VTS was modeled as a non-deterministic C-program manipulating an annotated graph. 
%
The special annotations \textit{assumes} and \textit{assertions} of CBMC's front end were used to express constraints on the model and properties to be checked. 
%
%The fusion rules and steady state properties were expressed as constraints using special annotations \textit{assumes}. 
%		
%The correspondence relationship between connectedness conditions and steady state were expressed as annotations \textit{assertions} to be checked. 
Using the tool's interface user can select the variation of the VTS, connectivity of the graph and other required parameters like an exploration depth.
%
The {\sattool} verifies the properties by first converting the constraints and properties into a Boolean formula and determine the satisfiability of the formula with the help of a SAT solver backend.
%
The satisfying model is translated into a human readable format and in case of a violation, the tool produces a readable counterexample.
%  following steps:
%	\begin{itemize}
%	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
%depth iff the Boolean formula is valid.
%	\item Check (using a SAT solver) validity of the verification condition. {\sattool} reports successful verification if the formula is found to be valid. If not, then {\sattool} produces a counterexample,
%an assignment to the variables of the model, that is a witness to the violation of the property.
%	\end{itemize}
For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat} and CryptoMiniSat~\cite{soos2016cryptominisat}.
% the winner of SAT 2015 Competition~\cite{balyo2016sat}.

@@

\subsubsection{{\ourtool} (QBF based synthesis tool)}
The synthesis encodings (Section~\ref{enc:synth}) is implemented  in~\ourtool.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS using the {\qbftool} interface. 
%
The tool can synthesize the queries discussed earlier and also their combinations.
%The tool can not only synthesize the discussed queries, but also their combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.
%
The tool returns a complete VTS with visual graph representation as an output to the user.

@@

\input{table3}
The minimal connectivity results for each variation of the existential condition are presented in Table~\ref{tab:smt-grph}.
%
The steady-state constraint requires that the structure of the graph is at least 2-connected. 
%
We found that 3-connectedness is the existential condition for the Boolean regulation model on vesicles, while 4-connectedness is the existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%
For all other constrained regulation models of VTS, the experimentation was unable to find any graphs representing the VTS in the stable state.
%
This strongly suggests that no such graphs exist, as our graphs are of finite size, this does not amount to a  proof.

@@

\input{table4}
%
Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
%
For this comparison, we have fixed the total number of molecules minimum four times for each SNARE type of the node count. 
%
The maximum number of parallel edges is 2.
%
%For our analysis we relax the 3:1 requirement for the Q and R-SNARES and treat a Q-SNARE triple helix as a single complex as modelled in~\cite{shukla2017discovering}.
%
%The 
%
In the table M/O indicates the search results in out of memory, T/O indicates a time out and ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
%
As an example, the result of verifying the formula for variation C of 3-connected, 10 compartment graph took 1977.72 secs for a satisfying result.
%
In comparison, {\sattool} was unable to solve the instance and ran out of memory.
%
The recursive encoding also performed better for the cases where the instance was unsatisfiable (Variant A timing comparison).
%
Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the case of eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with the limits of our tools and found that {\smttool} was able to solve the constraints up to $18$ nodes.

\input{table5}
%\textbf{Universal Condition:}

Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
%
The result of the graph connectivity for each variation of the VTS is shown.  
%
For example, we found that the 3-connected graph satisfies the universal condition for the variation 2. 
%
Note that for this variation existential condition result was the 2-connected graph. 
%
For every other version, the results remained the same.
%
This implies that for every 3-connected graph there is a valid VTS that satisfies all the constraints of the system.
% 
For biological cells, this means that the whole space of 3-connected graphs is available for evolutionary exploration.
%
%The experimentations were done using two QBF solvers: \depqbf and \rarqbf.

%(there is a satisfying assignments to satisfy constraints of VTS) is valid VTS.   
%\textbf{Synthesis}:
\input{table6}

We have applied~\ourtool~on seven partially defined VTSs.
%
The results are presented in Table~\ref{tab:synth-graph} for both the solvers
\depqbf and \zthree.
%
To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
quantifier-free.
%
The first four and the sixth VTSs are synthetic but inspire from literature for
typical motifs in VTSs. 
%
The third VTS is a subgraph of the last VTS.
%
%
The fifth VTS is taken from~\cite{burri2004complete}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.  
%
The figure shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.

In the Table~\ref{tab:synth-graph}, we report five synthesis queries.
%
The first one only adds new labeled edges to the graph.
%
We have ranked the all possible graph edits with the simple rank of
minimum updates.
% %
% Our tools were able to complete the graphs by adding five new edges
% and nine new molecules in 210s.
%
The second query adds new labels to the edge.
%
The third query synthesizes NNF Boolean functions only containing
$\land$ and $\lor$ gates for activity functions, while allowing
more edges to be added.
%
The result shows the basic template of 4 leaves and 3 gates.
%
To illustrate the versatility of our tool, the fourth query
synthesizes $3$-CNF functions (encoding not presented).
%
Finally, we report queries that allow both addition and deletion of edges and labels of node and labels.

### 2019-06-15 papers/journal/fig3.tex
First Update for revision

%\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
%thick,main node/.style={circle,draw,font=\sffamily,minimum size=0.8cm}]
%\begin{scope}[]
%
%\node[main node] (1) {$s_{1}$};
%\node[main node] (2) [below left of=1] {$s_{2}$};
%\node[main node] (3) [below right of=1] {$s_{3}$};
%
%\path[every node/.style={font=\sffamily\small}]
%(3) edge node [left] {} (1)
%(1) edge [loop above] node {} ()
%(2) edge [loop above] node {} ()
%(1) edge node [right] {} (2)
%(2) edge node[right] {} (3)
%(3) edge[bend left, below] node{} (2);
%%(3) edge [bend right] node[right] {} (2)
%\end{scope}
 \begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
	  thick,main node/.style={rectangle,draw,rounded corners}]
	 % 	\begin{scope}[]
	  \node[main node, text width=1.5cm] (pm) {$\mathbf{N_{0}}$: { {$Q_{a5}$} 
	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}}};
	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}}};

	  %le <-> pm
	  \path (le) edge[bend right=55] node [above] {$Q_{b7}$, $Q_{c7}$} (pm);
	  \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=32] node [below] {{$R_{3}$}} (pm);
	  \path (pm) edge[bend left=30, text width=2.1cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} (ee);
	\end{tikzpicture}
	\caption{Input partial VTS} 
		 \label{fig:synth-vts1}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
	  thick,main node/.style={rectangle,draw,rounded corners}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node, text width=1.5cm] (pm) {$\mathbf{N_{0}}$: { {$Q_{a5}$} 
	  	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}}...};
	  	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}}...};
	  	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}}...};

	  %le <-> pm
	  	  \path (le) edge[bend right=45] node [above] {$Q_{b7}$, $Q_{c7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
	%  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);

	  %le <-> ee
	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {{\color{blue} { {\textbf{{$R_{8}$}}}}}{\color{black},} {\color{blue} {$Q_{a7}$}}} (ee);
	  }}
	  %ee -> le
	   \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);
%	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {{R8}, Qa7, Qbc7,R7} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$ $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{    $R_{3}$}}} (ee);
%	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
	 % \end{scope}

	 \end{tikzpicture}
	 \caption{Output complete VTS} 
	 \label{fig:synth-vts2}
  \end{subfigure}%
  \caption{An example of synthesis of edge and molecules in the partial VTS.} \label{fig:synth-vts}
\end{figure}

>>>>

%\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2cm,
%thick,main node/.style={circle,draw,font=\sffamily,minimum size=0.8cm}]
%\begin{scope}[]
%
%\node[main node] (1) {$s_{1}$};
%\node[main node] (2) [below left of=1] {$s_{2}$};
%\node[main node] (3) [below right of=1] {$s_{3}$};
%
%\path[every node/.style={font=\sffamily\small}]
%(3) edge node [left] {} (1)
%(1) edge [loop above] node {} ()
%(2) edge [loop above] node {} ()
%(1) edge node [right] {} (2)
%(2) edge node[right] {} (3)
%(3) edge[bend left, below] node{} (2);
%%(3) edge [bend right] node[right] {} (2)
%\end{scope}
 \begin{tikzpicture}[->,>=stealth', auto , node distance=3.1cm,
	  thick,main node/.style={rectangle,draw,rounded corners}]
	 % 	\begin{scope}[]
	  \node[main node, text width=1.5cm] (pm) {$\mathbf{N_{0}}$: { {$Q_{a5}$} 
	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}} ...};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}} ...};
	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}} ...};

	  %le <-> pm
	  \path (le) edge[bend right=55] node [above] {$Q_{bc7}$} (pm);
	  \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{bc7}$, $R_{7}$} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=32] node [below] {{$R_{3}$}} (pm);
	  \path (pm) edge[bend left=30, text width=2.1cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$, $R_{7}$, $Q_{a2}$} (ee);
	\end{tikzpicture}
	\caption{Input partial VTS} 
		 \label{fig:synth-vts1}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.5cm,
	  thick,main node/.style={rectangle,draw,rounded corners}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node, text width=1.5cm] (pm) {$\mathbf{N_{0}}$: { {$Q_{a5}$} 
	  	  		                     {$Q_{a7}$} {$Q_{bc2}$} {$Q_{bc7}$}} ...};
	  	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {$\mathbf{N_{1}}$: { {$Q_{a2}$} {$ Q_{b2/3} $} {$ Q_{c2/3} $}} ...};
	  	  \node[main node, text width=1.3cm] (le) [above of=ee,yshift=-10mm,xshift=20mm] {$\mathbf{N_{2}}$: { {$Q_{a8}$} {$Q_{b8}$} {$Q_{c8}$}} ...};

	  %le <-> pm
	  	  \path (le) edge[bend right=45] node [above] {$Q_{bc7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
	%  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);

	  %le <-> ee
	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {{\color{blue} { {\textbf{{$R_{8}$}}}}}{\color{black},} {\color{blue} {$Q_{a7}$}}} (ee);
	  }}
	  %ee -> le
	   \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{bc7}$, $R_{7}$} (le);
%	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {{R8}, Qa7, Qbc7,R7} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, \\ {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$}, $Q_{bc7}$ $R_{7}$, $Q_{a2}$, \color{blue} {$R_{3}$}} (ee);
%	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
	 % \end{scope}

	 \end{tikzpicture}
	 \caption{Output complete VTS} 
	 \label{fig:synth-vts2}
  \end{subfigure}%
  \caption{An example of synthesis of edge and molecules in the partial VTS} \label{fig:synth-vts}
\end{figure}
